Analytic Doppler Imaging

### 2019-08-20 tex/ms.tex
more text, more figs

\subsection{Multiple spectral components}
%
In our discussion so far we have focused on the particular case where the
spectral/spatial decomposition of the stellar surface can be expressed as 
the outer product of two vectors (Equation~\ref{eq:inverse:azero}). As we
mentioned previously, this corresponds to the case where the spectrum is
constant across the surface of the star except for a spatially-variable 
amplitude: i.e., spots have the same spectrum as the rest of the star, but
emit less flux overall. However, most of the formalism developed here also
applies to the more general case where the spectrum at a particular point
on the surface of the star is a linear combination of $P$

\begin{align}
    \azero &= \mathrm{vec}\left( \bvec{A_0} \right) \nonumber \\
           &= \mathrm{vec}\left( \bvec{S} \, \bvec{Y}^\top \right) \quad,
\end{align}

@@

@@

\section{Performance}
\label{sec:performance}

Evaluation of the model via Equation~(\ref{eq:deconv:F}) requires 
first the rotation of the $(\lmax + 1)^2$
$\kT$ kernels (each of length $W$) to the correct stellar 
rotational phase, an operation that scales approximately
as $W \lmax^3$,
followed by $(\lmax + 1)^2$
linear convolutions of the rotated $\kT$ kernels with the 
spectral components (each of length $K$), which scales
approximately as $W K \lmax^2$. Since typically $K \gg \lmax$,
the latter computation dominates and the entire evaluation 
takes $\mathcal{O}(W K \lmax^2)$ operations.

\section{Stuff we're not addressing}
%
Differential rotation and convective blueshift.

@@

>>>>

\subsection{Multiple spectral components}
\label{sec:eigen}
%
In our discussion so far we have focused on the particular case where the
spectral/spatial decomposition of the stellar surface can be expressed as 
the outer product of two vectors (Equation~\ref{eq:inverse:azero}). As we
mentioned previously, this corresponds to the case where the spectrum is
constant across the surface of the star except for a spatially-variable 
amplitude: i.e., spots have the same spectrum as the rest of the star, but
emit less flux overall. However, most of the formalism developed here also
applies to the more general case where the spectrum at a particular point
on the surface of the star is a linear combination of several different
spectral components. In this case, the map vector $\azero$
may be written as the sum over $J$ spectra $\bvec{s}_j$, each of which is dotted into
a different vector of spherical harmonic coefficients $\bvec{y}_j^\top$:
%
\begin{align}
    \label{eq:eigen:azero}
    \azero 
        &= 
        \sum_{j=0}^{J-1}\mathrm{vec}\left( \bvec{s}_j \, \bvec{y}_j^\top \right) \\
        &=
        \mathrm{vec}\left( \boldsymbol{\mathbb{S}} \, \boldsymbol{\mathbb{Y}}^\top \right) \quad,
\end{align}
%
where $\boldsymbol{\mathbb{S}}$ is the $(K' \times J)$ matrix whose columns are
the $J$ spectral components and $\boldsymbol{\mathbb{Y}}^\top$ is the
$(J \times N)$ matrix whose rows are the corresponding $J$ spherical harmonic
coefficient vectors.

The model remains linear in both the spherical harmonic coefficients and the
spectral components, and the procedures outlined in \S\ref{sec:inverse} may
still be followed to solve the inverse problem, provided we unroll these
matrices into vectors, letting
$\mathbf{s} = \mathrm{vec}(\boldsymbol{\mathbb{S}})$
and
$\mathbf{y} = \mathrm{vec}(\boldsymbol{\mathbb{Y}})$.
A detailed discussion of this general case is deferred to future work,
but we present an example of a two-component stellar spectrum in the
examples section below.

@@

\begin{figure}[h!]
    \begin{centering}
    \includegraphics[width=0.98\linewidth]{figures/snr.pdf}
    \oscaption{snr}{%
        Recovered \spot map as a function of SNR per resolution element.
        \label{fig:snr}
    }
    \end{centering}
\end{figure}

@@

\section{Performance}
\label{sec:performance}
%
\xxx{In progress...}
Evaluation of the model via Equation~(\ref{eq:deconv:F}) requires 
first the rotation of the $(\lmax + 1)^2$
$\kT$ kernels (each of length $W$) to the correct stellar 
rotational phase, an operation that scales approximately
as $W \lmax^3$,
followed by $(\lmax + 1)^2$
linear convolutions of the rotated $\kT$ kernels with the 
spectral components (each of length $K$), which scales
approximately as $W K \lmax^2$. Since typically $K \gg \lmax$,
the latter computation dominates and the entire evaluation 
takes $\mathcal{O}(W K \lmax^2)$ operations.

\section{Stuff we're not addressing}
%
\xxx{In progress...}
Differential rotation and convective blueshift.

@@

    $J$                      & \# of spectral components                             & \\
